\documentclass[11pt,a4paper,roman,english,colorlinks,linkcolor=true]{moderncv}
\moderncvstyle{classic}%'casual', 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}%'blue', 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
\usepackage{xcolor}
\usepackage[url=false,
backend=bibtex,
style=numeric,
doi=true,
isbn=true,
backref=false,
maxnames=99,
defernumbers=true,
natbib=true,
sorting=ydnt]{biblatex}
\usepackage{refcount}
\DeclareNameAlias{author}{last-first}
\defbibenvironment{bibliography}
{\list
	{\printtext[labelnumberwidth]{%
			\printfield{labelprefix}%
			\printfield{labelnumber}}}
	{\setlength{\labelwidth}{\labelnumberwidth}%
		\setlength{\leftmargin}{5em}%
		\setlength{\labelsep}{\biblabelsep}%
		\addtolength{\leftmargin}{\labelsep}%
		\addtolength{\leftmargin}{\leftskip}%<----- here
		\setlength{\itemsep}{\bibitemsep}%
		\setlength{\parsep}{\bibparsep}}%
	\renewcommand*{\makelabel}[1]{\hss##1}}
{\endlist}
{\item}

%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Anjali}
\familyname{Suman}
\title{B. Sc., M. Sc.}
\address{Enschede, Netherlands} %{Netherlands}
\phone{+31-615228929}
\email{anjali.suman.stats@gmail.com}
\homepage{github.com/AnjaliML}
\quote{\textbf{Seeking Ph.D. positions in Machine Learning}}
\usepackage{lastpage}
\rfoot{\textit{\small{\color{gray}\thepage/\color{red}\pageref{LastPage}}}}

\begin{document}
	\hypersetup{
		colorlinks,
		linkcolor={red!50!black},
		citecolor={blue!50!black},
		urlcolor={blue}
	}
	%-----       resume       ---------------------------------------------------------
	\makecvtitle
	\cvitem{Updated On:}{\today}
	\section{\textbf{Research Interests}}
	\cvitem[-1em]{\textbf{Machine Learning}}{
		\hspace{-25mm}\cvlistdoubleitem{Computer vision}{Survival analysis}
		\hspace{-25mm}\cvlistdoubleitem{Physics aided machine learning}{Gradient descent algorithms}
		\hspace{-25mm}\cvlistdoubleitem{Sampling techniques}{Time series}
		\hspace{-25mm}\cvlistdoubleitem{Exploratory data analysis}{Data visualization}
	}
	
%	\section{\textbf{Education}}
%	\cventry{2018}{Master of Science in Statistics}{Hindu College, University of Delhi}{Delhi}{$59\%^{*}$}{$^{*}$percentile score of 80\%}
%	\cventry{2016}{Bachelor of Science in Statistics with Honors}{Ramanujan College, University of Delhi}{Delhi}{75\%}{}
%	\cventry{2013}{High School}{Krishna Niketan (CBSE)}{Patna, Bihar}{\textit{80\%}}{}
%	\cventry{2011}{Secondary School}{Krishna Niketan (CBSE)}{Patna, Bihar}{\textit{$9.2^{*}$}}{$^{*}$on a scale of 10}
	\section{\textbf{Education}}
	\cventry{2018}{Master of Science in Statistics}{Hindu College, University of Delhi}{Delhi}{}{}
	\cventry{2016}{Bachelor of Science in Statistics with Honors}{Ramanujan College, University of Delhi}{Delhi}{}{}
	\cventry{2013}{High School}{Krishna Niketan (CBSE)}{Patna, Bihar}{}{}
	\cventry{2011}{Secondary School}{Krishna Niketan (CBSE)}{Patna, Bihar}{}{}	
	
	\section{\textbf{Technical Skills}}
	\subsection{Python}
	\cvitem{}{PyTorch, Jupyter}
	\subsection{Computational Statistical Packages}
	\cvitem{}{R, SPSS, SAS (Basic knowledge)}
	\subsection{Computer Languages}
	\cvitem{}{C++, C}
	\subsection{Others}
	\cvitem{}{MATLAB, Octave, Ubuntu, \LaTeX}
	
	\section{\textbf{Work Experience}}
	\cvitem{June, 2022 -}{Oklahoma State University}
	\cvitem{Present}{Predicting machine failure using survival analysis and machine learning}
	\cvitem{\textbf{Mentor}}{Prof. Akash Deep}
	\cvitem{2019-20}{Sureland Industrial Fire Safety Limited}
	\cvitem{2017}{Cricnwin, Cheruniq Technology Pvt Ltd}

%	\pagebreak
	
\section{\textbf{Project Involvements}}
\subsection{Survival analysis \& machine learning}
\cvitem{\textbf{Mentor}}{Prof. Akash Deep}
\cvitem{2022}{
	\begin{itemize}
		\item This project aims to combine machine learning with survival analysis (bio-statistics) to predict the failure of machines in an industry. 
		\item We draw analogy between machine failure and survival analysis concepts. 
		\item We aim to implement a multi-event failure model to predict the survivability of machines in an industrial setting.
	\end{itemize}
}

\subsection{Inter-state migration pattern in India}
\cvitem{\textbf{GitHub:}}{\href{https://github.com/AnjaliML/InterStateMigrationIndia.git}{https://github.com/AnjaliML/InterStateMigrationIndia.git}}
\cvitem{2022}{
	\begin{itemize}
		\item We bring out a comparative picture of people migrating to neighboring states and the rest of the country.
		\item We find a list of the top 10 employing states.
		\item We bring out a clear picture of the gender ratio of workers migrating to a given state from states all over India.
	\end{itemize}
}

	\subsection{Sureland industrial fire safety limited}
	\cvitem{2019-20}{Design \& Analysis Department
		\begin{itemize}
%					\item Market analysis and improvement of product design and distribution.
%					\item The company specialized in fire safety. I was involved with the group that oversaw the design and distribution of smoke detectors. I used big data techniques to analyse fire accident statistics and the effectiveness of smoke detectors. An important aspect was also to judge and recommend the location of smoke detectors.
	\item The company specialized in fire safety. I used machine learning to analyse fire accident statistics and the effectiveness of smoke detectors. An important aspect was also to judge and recommend the location of smoke detectors.
			\end{itemize}
		}
	
	\subsection{Fantasy league score calculator}
	\cvitem{\textbf{GitHub:}}{\href{https://github.com/AnjaliML/FantasyCricket.git}{https://github.com/AnjaliML/FantasyCricket.git}}
	\cvitem{2017}{
		\begin{itemize}
					\item Determination of factors that affect the cricket's performance in a given match through confimatory factor analysis. 
					\item Determination of the weights of the contributions made by these factors on the value added by the player to his/her team.
					\item Prediction of the credit score of the individual players based on past records and the factors obtained through confirmatory factor analysis
			\end{itemize}
		}
	
		\subsection{Quality Assessment of Academic Website Using Sampling Techniques}
		\cvitem{\textbf{GitHub:}}{\href{https://github.com/AnjaliML/AcademicWebsiteSampling.git}{https://github.com/AnjaliML/AcademicWebsiteSampling.git}}
		\cvitem{\textbf{Mentor}}{Dr. Garima Priyadarshini}
		\cvitem{2016}{\begin{itemize}
						\item A Variety of studies has been conducted on websites.
						\item These studies are broadly based on heuristic analysis, surveys through questionnaires, interviews or web analysis tools (like Google analytics).
						\item We made a hypothesis according to questionnaire and analyze them through responses using some sampling techniques
				\end{itemize}}
		
			
			
%				\cvitem{2014}{Matchstick game}
%				\cvitem{}{\begin{itemize}
%								\item A game between a computer and an user such that the computer is always a winner.
%								\item Rules of game: (a) There are 21 matchsticks, (b) Player and computer can choose matchsticks alternatively, (c) At a chance they can pick less than 5 and greater than 0 matchsticks and (d) Whoever is forced to pick up the last matchstick loses the game.
%						\end{itemize}}
					
				
				\section{\textbf{Professional Development}}
				\cvitem{2015}{Indian Society of Agricultural Science: 68$^{th}$ Annual Conference.}
				\cvitem{2014}{IBM SPSS (Statistical Package for the Social Sciences) workshop.}
				\cvitem{2014}{INCOMECT (International Conference on Management Education \& Corporate Transformation)}
				\cvitem{2014}{Workshop on R-Language.}
				\cvitem{2014}{WinQSB for Operation Research workshop.}
				\cvitem{2013}{International DU conference.}

				\section{\textbf{Languages}}
				\cvitemwithcomment{English}{Fluent}{Daily practice, all work performed in English}
				\cvitemwithcomment{Hindi}{Native}{Mother Tongue}
									%
				\section{\textbf{Extra-Curricular}}
				\cvitem{2016}{Conference organizer team: Recent Statistical Computing Techniques and their applications}
											
				\section{\textbf{References}}
				\begin{tabular}{lr}
					% Referee 1
					\begin{minipage}[t]{3in}
						Prof. Akash Deep\\
						Assistant Professor\\
						Oklahoma State University\\
						\href{mailto:akash.deep@okstate.edu}{akash.deep@okstate.edu}
					\end{minipage}
					&
					% Referee 2
					\begin{minipage}[t]{3in}
						Prof. Vijay Kumar Pandey\\
						Assistant Professor\\
						Bareilly College\\
						\href{mailto:vijay.pandey550@gmail.com}{vijay.pandey550@gmail.com}
					\end{minipage}
				\end{tabular}
\end{document}
